Model LF

### 2022-12-12 Power point test.Rmd
Commit

```{r}
plot(((u_ds_02 - u_ds_bs2)), col= "black", xlab= "Year", ylab= "Ændring i capacaty utilization", main= "Capacity utilization");
grid()
```

>>>>

```{r}
plot(((u_ds_02 - u_ds_bs2)), col= "black", xlab= "Year", ylab= "Ændring i capacaty utilization", main= "Capacity utilization");
grid()

```{r}
plot(((xk_ds_02 - xk_ds_bs2)), col= "black", xlab= "Year", ylab= "Ændring i capacaty utilization", main= "Capacity utilization");
grid()

plot(((mk_ds_02 - mk_ds_bs2)), col= "black", xlab= "Year", ylab= "Ændring i capacaty utilization", main= "Capacity utilization");
grid()
```

### 2022-12-12 max_dp endogen stød.Rmd
Commit

@@

@@

```
```{r}
plot(((unemp_05 - unemp_bs56)*1000), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Sensitivity of Unemployment", ylim= c(0,25000));
lines(((unemp_07b - unemp_bs7b)*1000), col= "red");
lines(((unemp_03 - unemp_bs3)*1000 ), col= "green");
legend("left", legend=c("All channels", "All channels but productivity","Productivity channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue", "red", "green"));
grid()
```

>>>>

```{r}
plot(prod_000, col= "red"); lines(prod_bs1, col = "blue");
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "blue")); 
grid()

prod_000 - prod_bs1

@@

```{r}
plot(((prodk_07b - prodk_bs7b)), col= "blue", xlab= "Year", ylab= "Change in Government net lending", main= "Change in Government net-lending")
```

@@

```{r}
plot(((unemp_05 - unemp_bs56)*1000), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Sensitivity of Unemployment", ylim= c(0,25000));
lines(((unemp_07b - unemp_bs7b)*1000), col= "red");
lines(((unemp_03 - unemp_bs3)*1000 ), col= "green");
legend("left", legend=c("All channels", "All channels but productivity","Productivity channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue", "red", "green"));
grid()
```
